Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-15 chapters/introduction/introduction.tex
background 2

\subsection{Geo-Calibration}
%\todo{add deterministic methods}
%
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually the geo-calibration task is
straightforward: given an image, identify the time and the location it
was captured in the world and the direction the camera was facing.
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.

@@

\item \textbf{Time Estimation:}
Matzen and Snavely~\cite{matzen2014scene} predict
timestamps for photos by matching against a time-varying
reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
time of the day by measuring the light intensity profiles captured by
cameras.~\cite{salem2016face2year,ginosar2015century} propose to date the
year book photos by analyzing human appearance. Lee
\etal~\cite{linking2015iccp} find visual paterns in the buildings,
relate them to certain time periods.

@@

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great a help for
researchers to conquer the problems like geo-localization and camera
calibration.
Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
network to predict the geographic location of the input
image.~\cite{walch2017image} applies LSTM on CNN features learned for
camera localization.

Closely related to camera geo-calibration, studies also have been done
to identify the camera poses and focal length using deep neural
networks.
Horizon line is an important indicator for estimating camera poses,
which is, giving the focal length, one can derive the camera roll and
pitch angles from the horizon line position in the image.
Work~\cite{zhai2016horizon, workman2016horizon, hold2017perceptual}
has been done to to identify the horizon line with CNNs.  Workman
\etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
neural network that can identify 6-DOF camera parameters, but their
method only limited to specific scenes.

>>>>

\subsection{Geo-Calibration}
%\todo{add deterministic methods}
%
Automatic image geo-calibration continues to grow in importance as a
direct result of the increasing amount of imagery available
via the Internet. Conceptually the geo-calibration task is
straightforward: given an image, identify the time and the location it
was captured in the world and the direction the camera was facing.
Solving this problem is of great value for a wide variety of fields,
with potential applications ranging from the forensic
sciences~\cite{stylianou13jane} to environmental
monitoring~\cite{zhang2012mining}.
\todo{make it smoother}

@@

\item \textbf{Time Estimation:}
Matzen and Snavely~\cite{matzen2014scene} predict
timestamps for photos by matching against a time-varying
reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
time of the day by measuring the light intensity profiles captured by
cameras. Methods are proposed to date the
year book photos by analyzing human
appearance~\cite{salem2016face2year,ginosar2015century}. Lee
\etal~\cite{linking2015iccp} find visual paterns in the buildings,
relate them to certain time periods.
\newline

\item \textbf{Camera Pose Estimation:}
\todo{}

@@

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas. 
It is widely accepted that DNNs have excellent performance in
high-level visual feature learning.
This valuable ability provides researchers powerful tools to
solve the challenging geo-calibration tasks.
Weyand and Kostrikov \etal~\cite{planet} propose a convolutional
network to predict the geographic location of the input
image. Walch \etal~\cite{walch2017image} aggregate learned CNN
features with LSTM to generate global image representation for camera
localization.  In pose estimation aera, Work~\cite{zhai2016horizon,
workman2016horizon, hold2017perceptual} has been done to to identify
the horizon line with CNNs (one can derive the camera roll and pitch
angles from the horizon line position giving the camera focal length).

Closely related to camera geo-calibration, studies also have been done
to identify the camera intrinsics using deep neural networks.
Workman \etal~\cite{workman2015deepfocal} develop a CNN to estimate the camera
focal length. Kendall \etal~\cite{kendall2015convolutional} propose a
neural network that can identify 6-DOF camera parameters, but their
method only limited to specific scenes.
